Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-02-13 manuscript/text_reuse.tex
finished policy similarity section

Active within a domain, but possibly moving the status quo in opposite directions. (Glick)
Moving the status quo in a uniform direction, but with different specific policies. (berry berry)
Qualitative classification of the properties of bills adopted within a policy domain (Volden 2006)
Quantitative coding of an important dimension of legislation (e.g., abortion bill restrictiveness) (Mooney and Lee 1992)

Drawing upon this general concept of similarity, we derive three empirical expectations regarding the behavior of text re-use as an effective measure of policy similarity. These will serve as validity tests going forward.

>>>>

In past work on policy adoption, researchers have drawn upon varying levels of similarity to define the policies of focus. Perhaps the broadest approach---studying policies adopted within a domain, but moving the status quo in opposite directions---is represented by \citet{glick1992judicial}. Glick studies judicial enactments related to the ``right to die''---the right of patients or their representatives to end the use of life-preserving medical technology. He considers an adoption to include any judicial enactment on this topic, whether they restrict medical providers' deference to the patients or enact broad patients' rights.  \citet{berry1990} look at policy change in a uniform direction---states' adoption of lotteries. Lotteries, of course, vary in terms of their rules and financial models, but all of the policies studied by \citet{berry1990} moved the status quo from no state lottery to the existence of a state lottery. \citet{volden2006} considers a broad array of state laws---those implemented for the Federal Health and Human Services Children's Health Insurance Program (CHIP). CHIP laws were coded for six policy characteristics and then analyzed for diffusion dynamics. Lastly, \citet{mooney1995legislative} provides an example of quantitative coding of policies adopted in a given domain. They code the permissiveness of state abortion laws (pre Roe v. Wade) on a five-point scale. These examples convey the variability with which scholars have defined the set of policies that are considered suitable for comparison in policy adoption studies.

Drawing upon this general concept of similarity, we see that policies that are considered comparable in the context of diffusion exhibit two qualities. First, they often, but do not always, move the status quo in a similar direction. This could be thought of as ideological similarity. Second, they enact policy in similar domains---either narrowly or broadly conceived. If measuring text re-use is an effective measure of the concepts underlying policy diffusion, we should see the volume of text re-use correlate with the ideological and policy domain similarities of state bills. We will revisit these two dimensions when describing our validation tests below. But first we define the algorithms we use for the analysis of text reuse.
